---
title: "Average habitat quality and area burned"
author: "Jessalyn Ayars"
date: '2022-06-27'
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(terra)
library(here)
library(tidyverse)
library(furrr)
select <- dplyr::select
```

## example workflow
```{r}
fire <- rast(here("data", "output_data", "ravg", "cbi4_ca-brick_2021_11.1.tif")) 
sp <- rast(here("data", "output_data", "hab-suit-post-4", "a031.tif"))

sp.fire.mask.all <- mask(sp, fire.all, maskvalues = c(NA, 0)) 
plot(sp.fire.mask.all)
hs.all <- global(sp.fire.mask.all, fun = "mean", na.rm = T) 
fire.sp.mask.all <- mask(fire.all, sp)
plot(fire.sp.mask.all)
hq.all <- global(fire.sp.mask.all, fun = "sum", na.rm = T)
```

## chtc processing

### define jobs by
- year 2020/2021
- species (650)
- quality/quantity
- ecoregion

## analysis by ecoregion
```{r}
ecoregions.list <- list.files(here("data", "output_data", "hab-suit-post-4")) %>% as_tibble() %>%
  mutate(a = "cbi4_ca-brick_2020_11.1.tif", b = "cbi4_ca-brick_2020_10.1.tif", c = "cbi4_ca-brick_2020_10.2.tif", d = "cbi4_ca-brick_2020_7.1.tif", e = "cbi4_ca-brick_2020_6.2.tif", f = "cbi4_ca-brick_2021_11.1.tif", g = "cbi4_ca-brick_2021_10.1.tif", h = "cbi4_ca-brick_2021_10.2.tif", i = "cbi4_ca-brick_2021_7.1.tif", j = "cbi4_ca-brick_2021_6.2.tif") %>%
  pivot_longer(cols = a:j, names_to = NULL, values_to = "ravg") %>%
  mutate(which.a = "quantity", which.b = "quality") %>%
  pivot_longer(cols = which.a:which.b, names_to = NULL, values_to = "which")
write_csv(ecoregions.list, here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F)
ecoregions.list[1:8640,] %>%
  write_csv(here("code", "chtc-analysis-ecoregions.txt"), col_names = F)
```

### take 2 with more memory
- wrote 2nd half, when ready to run write 1st half 
```{r}
all <- read_csv(here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F)
take2 <- all %>%
  mutate(out.name = str_c(X1, "_", X2, "_", X3, ".csv")) %>%
  anti_join(list.files((here("results", "ecoregions-output"))) %>% as_tibble(), by = c("out.name" = "value")) %>%
  select(-out.name)
write_csv(take2[1:5000,], here("code", "chtc-analysis-ecoregions-part1.txt"), col_names = FALSE)
```

### take 3 with more memory and disk
```{r}
all <- read_csv(here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F)
take3 <- all %>%
  mutate(out.name = str_c(X1, "_", X2, "_", X3, ".csv")) %>%
  anti_join(list.files((here("results", "ecoregions-output"))) %>% as_tibble(), by = c("out.name" = "value")) %>%
  select(-out.name)
write_csv(take3, here("code", "chtc-analysis-ecoregions.txt"), col_names = FALSE)
```

### take 4 with more memory and disk
- doing 1st 1000 on desktop
```{r}
all <- read_csv(here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F)
take4 <- all %>%
  mutate(out.name = str_c(X1, "_", X2, "_", X3, ".csv")) %>%
  anti_join(list.files((here("results", "ecoregions-output"))) %>% as_tibble(), by = c("out.name" = "value")) %>%
  select(-out.name)
write_csv(take4[1000:7088,], here("code", "chtc-analysis-ecoregions.txt"), col_names = FALSE)
```

### using parallel processing on desktop too
```{r}
### fxn for map
ecoregion_stats <- function(sp.in, cbi4.in, type) {
  sp <- rast(here("data", "output_data", "hab-suit-post-4", sp.in))
  cbi4 <- rast(here("data", "output_data", "ravg", cbi4.in))
  
  if (type == "quality") {
	  qual.rast <- mask(sp, cbi4, maskvalues = c(NA, 0))
	  stats <- global(qual.rast, fun = "mean", na.rm = T)
  } else {
	  quant.rast <- mask(cbi4, sp)
	  stats <- global(quant.rast, fun = "sum", na.rm = T)
  }

  write_csv(stats, here("results", "ecoregions-output-desktop", str_c(sp.in, "_", cbi4.in, "_", type, ".csv")))
}
###

### doing it in parallel
plan(multisession, workers = 4)
future_pwalk(list(take4$X1[4:1000], take4$X2[4:1000], take4$X3[4:1000]), ecoregion_stats)
###
```

### take 5, on desktop
- this means the previous params worked pretty well in chtc to get all the jobs run (finally!)
```{r}
all <- read_csv(here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F)
take5 <- all %>%
  mutate(out.name = str_c(X1, "_", X2, "_", X3, ".csv")) %>%
  anti_join(list.files((here("results", "ecoregions-output"))) %>% as_tibble(), by = c("out.name" = "value")) %>%
  select(-out.name) 

plan(multisession, workers = 4)
future_pwalk(list(take5$X1, take5$X2, take5$X3), ecoregion_stats)
```

### take 6 
- redoing 7.1, 11.1, 6.2 since they had area cut off 
- wrote 4/25, not run yet
```{r}
all <- read_csv(here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F)
take6 <- all %>%
  mutate(out.name = str_c(X1, "_", X2, "_", X3, ".csv")) %>%
  anti_join(list.files((here("results", "ecoregions-output"))) %>% as_tibble(), by = c("out.name" = "value")) %>%
  select(-out.name)
write_csv(take6, here("code", "chtc-analysis-ecoregions.txt"), col_names = FALSE)
```

### take 7, on desktop
- 4/29: ready to go once chtc output arrives on desktop
- 5/5 running again: still need 103
- 5/9 continuing to deal with the mysterious R error
```{r}
all <- read_csv(here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F)
take7 <- all %>%
  mutate(out.name = str_c(X1, "_", X2, "_", X3, ".csv")) %>%
  anti_join(list.files((here("results", "ecoregions-output"))) %>% as_tibble(), by = c("out.name" = "value")) %>%
  select(-out.name) # so tiny!

ecoregion_stats <- function(sp.in, cbi4.in, type) {
  sp <- rast(here("data", "output_data", "hab-suit-post-4", sp.in))
  cbi4 <- rast(here("data", "output_data", "ravg", cbi4.in))
  
  if (type == "quality") {
	  qual.rast <- mask(sp, cbi4, maskvalues = c(NA, 0))
	  stats <- global(qual.rast, fun = "mean", na.rm = T)
  } else {
	  quant.rast <- mask(cbi4, sp)
	  stats <- global(quant.rast, fun = "sum", na.rm = T)
  }

  write_csv(stats, here("results", "ecoregions-output-desktop", str_c(sp.in, "_", cbi4.in, "_", type, ".csv")))
}

plan(multisession, workers = 3)
future_pwalk(list(take7$X1, take7$X2, take7$X3), ecoregion_stats) # nope

walk(list(take7$X1[1], take7$X2[1], take7$X3[1]), ecoregion_stats) # nope (can't find cbi4.in)
ecoregion_stats(take7$X1[1], take7$X2[1], take7$X3[1]) # nope (aborts R)

# outside of any fanciness
sp <- rast(here("data", "output_data", "hab-suit-post-4", take7$X1[3]))
cbi4 <- rast(here("data", "output_data", "ravg", take7$X2[3]))
type = take7$X3[3]
quant.rast <- mask(cbi4, sp) # aborts for jobs 1 and 3 at least
quant.rast.2 <- crop(cbi4, sp, mask = T, touches = F) # aborts
stats <- global(quant.rast, fun = "sum", na.rm = T)

write_csv(stats, here("results", "ecoregions-output-desktop", str_c(sp.in, "_", cbi4.in, "_", type, ".csv")))

# attempting it in chtc
write_csv(take7, here("code", "chtc-analysis-ecoregions.txt"), col_names = FALSE)

# all that's left is b127: what's wrong with it? (american kestrel) (some b127 succeeded on 4/14)
b127 <- rast(here("data", "output_data", "hab-suit-post-4", "b127.tif"))
plot(b127) # corrupted ? in both CHTC and the desktop, sometime since 4/14? 
b127.3 <- rast(here("data", "output_data", "b127.tif")) # checking version from step 3
plot(b127.3)
```

### bringing ecoregions output back together
```{r}
files.out <- list.files(here("results", "ecoregions-output"))
chtc.results <- as_tibble(files.out) %>%
  rename(filename = value) %>%
  mutate(temp.str = str_split_fixed(filename, "_", n = 6)) %>%
  mutate(CHWR_ID = str_sub(temp.str[,1], start = 1, end = 4), 
         year = temp.str[,4], 
         ecoregion = str_sub(temp.str[,5], start = 1, end = -5),
         which = str_sub(temp.str[,6], start = 1, end = -5), 
         cbi.1 = NA, cbi.2 = NA, cbi.3 = NA, cbi.4 = NA) %>%
  select(-temp.str)

for (i in 1:nrow(chtc.results)) {
  temp <- read_csv(here("results", "ecoregions-output", files.out[i]))
  chtc.results$cbi.1[i] <- unlist(temp[1,])
  chtc.results$cbi.2[i] <- unlist(temp[2,])
  chtc.results$cbi.3[i] <- unlist(temp[3,])
  chtc.results$cbi.4[i] <- unlist(temp[4,])
}

write_csv(chtc.results, here("results", "results_ecoregions_raw.csv"))
```

### quality control
```{r}
# alt. duplicates
chtc.results %>% group_by(CHWR_ID, year, ecoregion, which) %>%
  mutate(how.many = n()) %>%
  filter(how.many > 1)  # no duplicates
# looking at the NAs
results.na <- chtc.results %>%
  filter(is.na(cbi.1)|is.na(cbi.2)|is.na(cbi.3)|is.na(cbi.4))
# fine to have NAs, be concerned if they are in cbi.1 but NOT others (no cases of this)
results.na.2 <- filter(results.na, is.na(cbi.1) & (!is.na(cbi.2)|!is.na(cbi.3)|!is.na(cbi.4)))
# cases where there are NAs in cbi > 1 but not cbi.1? how would that happen?
results.na.3 <- filter(results.na, !is.na(cbi.1)) 
# these are places where there is only habitat in unburned areas, so burn indexes yield NA for quality
level.2 <- st_read(here("data", "raw_data", "NA_CEC_Eco_Level2.shp")) %>%
  st_transform(crs(na.3.test.sp))
na.3.test.sp <- rast(here("data", "output_data", "hab-suit-post-4", "a002.tif"))
plot(na.3.test.sp)
plot(level.2$geometry, add = T)
max(results.na.3$cbi.1) 
# only drop rows with NAs all the way across

# outside range for quality
range.check <- filter(chtc.results, which == "quality") %>% 
  drop_na() %>%
  filter(cbi.1 > 100 | cbi.2 > 100 | cbi.3 > 100 | cbi.4 > 100 | 
           cbi.1 < 0 | cbi.2 < 0 | cbi.3 < 0 | cbi.4 < 0) # none

# why are there 9 more than expected?
all <- read_csv(here("code", "chtc-analysis-ecoregions-backup.txt"), col_names = F) %>%
  mutate(out.name = str_c(X1, "_", X2, "_", X3, ".csv"))
extras <- chtc.results %>% anti_join(all, by = c("filename" = "out.name")) 
# b378 quantity was still in the list for some reason, deleted
```

### write
```{r}
test <- chtc.results %>%
  filter(!is.na(cbi.1)|!is.na(cbi.2)|!is.na(cbi.3)|!is.na(cbi.4))

write_csv(test, here("results", "results_ecoregion.csv"))
```

## area burned summaries
- getting area burned by categories of interest: ecoregion (done in ravg summary), fire severity (done in ravg summary), SGCN, taxa
- first, get a list of sp in the category of interest
- second, create a raster that is presence/absence of category of interest
  - sum: >? number doesn't matter but not 0/na does
- third, mask fire w/ this and get a global sum

### SGCN area
```{r}
# generating lists
sp.metadata <- read_csv(here("data", "output_data", "species-metadata-final.csv"))
sgcn.yes.list <- sp.metadata %>% filter(SGCN == 1) %>%
  mutate(filename = str_c(tolower(CWHR_ID), ".tif")) %>%
  select(filename) %>%
  semi_join(as_tibble(list.files(here("data", "output_data", "hab-suit-post-4"))), by = c("filename" = "value"))
sgcn.no.list <- sp.metadata %>% filter(SGCN == 0) %>%
  mutate(filename = str_c(tolower(CWHR_ID), ".tif")) %>%
  select(filename)  %>%
  semi_join(as_tibble(list.files(here("data", "output_data", "hab-suit-post-4"))), by = c("filename" = "value"))

# getting presence/absence rasters (max habitat suitability)
sgcn.yes.rast <- rast(here("data", "output_data", "hab-suit-post-4", sgcn.yes.list[1,]))
for (i in 2:nrow(sgcn.yes.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", sgcn.yes.list[i,]))
  sgcn.yes.rast <- mosaic(sgcn.yes.rast, temp, fun = "max")
  i
} 
writeRaster(sgcn.yes.rast, here("data", "output_data", "sgcn_yes.tif")) 

sgcn.no.rast <- rast(here("data", "output_data", "hab-suit-post-4", sgcn.no.list[1,])) # too big to finish
for (i in 2:nrow(sgcn.no.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", sgcn.no.list[i,]))
  sgcn.no.rast <- mosaic(sgcn.no.rast, temp, fun = "max")
  i
}
# trying rest of it
for (i in 246:nrow(sgcn.no.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", sgcn.no.list[i,]))
  sgcn.no.rast <- mosaic(sgcn.no.rast, temp, fun = "max")
  i
}
writeRaster(sgcn.no.rast, here("data", "output_data", "sgcn_no_1-249.tif"))
sgcn.no.rast <- rast(here("data", "output_data", "sgcn_no_1-249.tif"))
for (i in 250:nrow(sgcn.no.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", sgcn.no.list[i,]))
  sgcn.no.rast <- mosaic(sgcn.no.rast, temp, fun = "max")
  i
}
writeRaster(sgcn.no.rast, here("data", "output_data", "sgcn_no.tif"))
# global sum w/fire, by ecoregion & year
ecoregion_stats2 <- function(sp.in, cbi4.in) {
  sp <- rast(here("data", "output_data", sp.in))
  cbi4 <- rast(here("data", "output_data", "ravg", cbi4.in))
	quant.rast <- mask(cbi4, sp)
	stats <- global(quant.rast, fun = "sum", na.rm = T)
  write_csv(stats, here("results", "area-output", str_c(sp.in, "_", cbi4.in, "_", ".csv")))
}

sgcn.jobs <- as_tibble(x = c("sgcn_yes.tif", "sgcn_no.tif")) %>%  
   mutate(a = "cbi4_ca-brick_2020_11.1.tif", b = "cbi4_ca-brick_2020_10.1.tif", c = "cbi4_ca-brick_2020_10.2.tif", d = "cbi4_ca-brick_2020_7.1.tif", e = "cbi4_ca-brick_2020_6.2.tif", f = "cbi4_ca-brick_2021_11.1.tif", g = "cbi4_ca-brick_2021_10.1.tif", h = "cbi4_ca-brick_2021_10.2.tif", i = "cbi4_ca-brick_2021_7.1.tif", j = "cbi4_ca-brick_2021_6.2.tif") %>%
  pivot_longer(cols = a:j, names_to = NULL, values_to = "ravg") %>%
  filter(value == "sgcn_no.tif") # for 2nd half

plan(multisession, workers = 4)
future_pwalk(list(sgcn.jobs$value, sgcn.jobs$ravg), ecoregion_stats2)
```

#### sgcn output back together
```{r}
sgcn.out <- list.files(here("results", "area-output"), pattern = "sgcn")

sgcn.results <- as_tibble(sgcn.out) %>%
  rename(filename = value) %>%
  mutate(temp.str = str_split_fixed(filename, "_", n = 6)) %>%
  mutate(sgcn = str_sub(temp.str[,2], start = 1, end = -5), 
         year = temp.str[,5], 
         ecoregion = str_sub(temp.str[,6], start = 1, end = -10),
         cbi.1 = NA, cbi.2 = NA, cbi.3 = NA, cbi.4 = NA) %>%
  select(-temp.str)

for (i in 1:nrow(sgcn.results)) {
  temp <- read_csv(here("results", "area-output", sgcn.out[i]))
  sgcn.results$cbi.1[i] <- unlist(temp[1,])
  sgcn.results$cbi.2[i] <- unlist(temp[2,])
  sgcn.results$cbi.3[i] <- unlist(temp[3,])
  sgcn.results$cbi.4[i] <- unlist(temp[4,])
}

write_csv(sgcn.results, here("results", "results_sgcn_raw.csv"))
```

### taxa area
```{r}
# generating lists
sp.metadata <- read_csv(here("data", "output_data", "species-metadata-final.csv")) %>%
  mutate(filename = str_c(tolower(CWHR_ID), ".tif")) %>%
  semi_join(as_tibble(list.files(here("data", "output_data", "hab-suit-post-4"))), by = c("filename" = "value"))
taxa.a.list <- sp.metadata %>% filter(TaxaGrp == "amphibian") %>%
  select(filename)
taxa.b.list <- sp.metadata %>% filter(TaxaGrp == "bird") %>%
  select(filename) 
taxa.m.list <- sp.metadata %>% filter(TaxaGrp == "mammal") %>%
  select(filename) 
taxa.r.list <- sp.metadata %>% filter(TaxaGrp == "reptile") %>%
  select(filename)

# getting presence/absence rasters (max habitat suitability)
taxa.a.rast <- rast(here("data", "output_data", "hab-suit-post-4", taxa.a.list[1,]))
for (i in 2:nrow(taxa.a.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", taxa.a.list[i,]))
  taxa.a.rast <- mosaic(taxa.a.rast, temp, fun = "max")
  i
}  
writeRaster(taxa.a.rast, here("data", "output_data", "amphibians.tif")) 

taxa.b.rast <- rast(here("data", "output_data", "hab-suit-post-4", taxa.b.list[1,]))
for (i in 2:nrow(taxa.b.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", taxa.b.list[i,]))
  taxa.b.rast <- mosaic(taxa.b.rast, temp, fun = "max")
  i
}  
writeRaster(taxa.b.rast, here("data", "output_data", "birds_1-180.tif"))
taxa.b.rast <- rast(here("data", "output_data", "birds_1-180.tif"))
for (i in 180:nrow(taxa.b.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", taxa.b.list[i,]))
  taxa.b.rast <- mosaic(taxa.b.rast, temp, fun = "max")
  i
}  
writeRaster(taxa.b.rast, here("data", "output_data", "birds.tif")) 

taxa.m.rast <- rast(here("data", "output_data", "hab-suit-post-4", taxa.m.list[1,]))
for (i in 2:nrow(taxa.m.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", taxa.m.list[i,]))
  taxa.m.rast <- mosaic(taxa.m.rast, temp, fun = "max")
  i
}  
writeRaster(taxa.m.rast, here("data", "output_data", "mammals_1-110.tif")) 
taxa.m.rast <- rast(here("data", "output_data", "mammals_1-110.tif"))
for (i in 110:nrow(taxa.m.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", taxa.m.list[i,]))
  taxa.m.rast <- mosaic(taxa.m.rast, temp, fun = "max")
  i
}
writeRaster(taxa.m.rast, here("data", "output_data", "mammal.tif")) 

taxa.r.rast <- rast(here("data", "output_data", "hab-suit-post-4", taxa.r.list[1,]))
for (i in 2:nrow(taxa.r.list)) {
  temp <- rast(here("data", "output_data", "hab-suit-post-4", taxa.r.list[i,]))
  taxa.r.rast <- mosaic(taxa.r.rast, temp, fun = "max")
  i
}  
writeRaster(taxa.r.rast, here("data", "output_data", "reptiles.tif")) 

taxa.jobs <- as_tibble(x = c("amphibians.tif", "birds.tif", "mammal.tif", "reptiles.tif")) %>% 
   mutate(a = "cbi4_ca-brick_2020_11.1.tif", b = "cbi4_ca-brick_2020_10.1.tif", c = "cbi4_ca-brick_2020_10.2.tif", d = "cbi4_ca-brick_2020_7.1.tif", e = "cbi4_ca-brick_2020_6.2.tif", f = "cbi4_ca-brick_2021_11.1.tif", g = "cbi4_ca-brick_2021_10.1.tif", h = "cbi4_ca-brick_2021_10.2.tif", i = "cbi4_ca-brick_2021_7.1.tif", j = "cbi4_ca-brick_2021_6.2.tif") %>%
  pivot_longer(cols = a:j, names_to = NULL, values_to = "ravg")

plan(multisession, workers = 4)
future_pwalk(list(taxa.jobs$value[20:40], taxa.jobs$ravg[20:40]), ecoregion_stats2) # running 2nd half since mammal.tif had a typo
```

#### taxa results back together
### area output back together
```{r}
temp <- list.files(here("results", "area-output")) 
taxa.out <- temp[str_detect(temp, pattern = "sgcn", negate = T)]

taxa.results <- as_tibble(taxa.out) %>%
  rename(filename = value) %>%
  mutate(temp.str = str_split_fixed(filename, "_", n = 6)) %>%
  mutate(taxa.grp = str_sub(temp.str[,1], start = 1, end = -5), 
         year = temp.str[,4], 
         ecoregion = str_sub(temp.str[,5], start = 1, end = -5),
         cbi.1 = NA, cbi.2 = NA, cbi.3 = NA, cbi.4 = NA) %>%
  select(-temp.str)

for (i in 1:nrow(taxa.results)) {
  temp <- read_csv(here("results", "area-output", taxa.out[i]))
  taxa.results$cbi.1[i] <- unlist(temp[1,])
  taxa.results$cbi.2[i] <- unlist(temp[2,])
  taxa.results$cbi.3[i] <- unlist(temp[3,])
  taxa.results$cbi.4[i] <- unlist(temp[4,])
}

write_csv(taxa.results, here("results", "results_taxa_raw.csv"))
```

## area burned in 2020 and 2021 (cumulative)
```{r}
ecoregions <- read_csv(here("results", "results_ecoregion_metadata.csv"))
cumu.jobs <- ecoregions %>%
  select(-cbi.1.quality, -cbi.2.quality, -cbi.3.quality, -cbi.4.quality) %>%
  rename(cbi.1 = "cbi.1.quantity",
         cbi.2 = "cbi.2.quantity",
         cbi.3 = "cbi.3.quantity",
         cbi.4 = "cbi.4.quantity") %>%
  group_by(CWHR_ID) %>% 
  mutate(cbi.1 = sum(cbi.1),
         cbi.2 = sum(cbi.2),
         cbi.3 = sum(cbi.3),
         cbi.4 = sum(cbi.4),
         sp.area = (cbi.1 + cbi.2 + cbi.3 + cbi.4)/2) %>%
  ungroup() %>%
  select(-ecoregion, -year) %>%
  distinct() %>%
  mutate(total.burned = cbi.2 + cbi.3 + cbi.4,
         prop.burned = total.burned/sp.area,
         prop.cbi.4 = cbi.4/sp.area,
         C_NAME = fct_reorder(as.factor(C_NAME), desc(prop.burned))) %>%
  ungroup() %>%
  arrange(desc(prop.burned)) %>%
  slice_head(n = 200) %>%
  mutate(filename = str_c(tolower(CWHR_ID), ".tif")) %>%
  select(filename)

cumu_area_stats <- function(sp.in) {
  sp <- rast(here("data", "output_data", "hab-suit-post-4", sp.in))
  cbi4 <- rast(here("data", "output_data", "ravg", "cbi4_ca-brick_202021_mosaic.tif"))
	quant.rast <- mask(cbi4, sp)
	stats <- global(quant.rast, fun = "sum", na.rm = T)
  write_csv(stats, here("results", "cumu-area-output", str_c(sp.in, "_cumu", ".csv")))
}

plan(multisession, workers = 4)
future_pwalk(list(cumu.jobs$filename), cumu_area_stats)

cumu.out <- list.files(here("results", "cumu-area-output")) 

cumu.results <- as_tibble(cumu.out) %>%
  rename(filename = value) %>%
  mutate(temp.str = str_split_fixed(filename, "_", n = 2)) %>%
  mutate(CWHR_ID = toupper(str_sub(temp.str[,1], start = 1, end = -5)), 
         cbi.1 = NA, cbi.2 = NA, cbi.3 = NA, cbi.4 = NA) %>%
  select(-temp.str)

for (i in 1:nrow(cumu.results)) {
  temp <- read_csv(here("results", "cumu-area-output", cumu.out[i]))
  cumu.results$cbi.1[i] <- unlist(temp[1,])
  cumu.results$cbi.2[i] <- unlist(temp[2,])
  cumu.results$cbi.3[i] <- unlist(temp[3,])
  cumu.results$cbi.4[i] <- unlist(temp[4,])
}

write_csv(cumu.results, here("results", "results_cumu_raw.csv"))
```

### getting the rest
```{r}
done <- list.files(here("results", "cumu-area-output"))

ecoregions <- read_csv(here("results", "results_ecoregion_metadata.csv"))
cumu.jobs <- ecoregions %>%
  select(-cbi.1.quality, -cbi.2.quality, -cbi.3.quality, -cbi.4.quality) %>%
  rename(cbi.1 = "cbi.1.quantity",
         cbi.2 = "cbi.2.quantity",
         cbi.3 = "cbi.3.quantity",
         cbi.4 = "cbi.4.quantity") %>%
  group_by(CWHR_ID) %>% 
  mutate(cbi.1 = sum(cbi.1),
         cbi.2 = sum(cbi.2),
         cbi.3 = sum(cbi.3),
         cbi.4 = sum(cbi.4),
         sp.area = (cbi.1 + cbi.2 + cbi.3 + cbi.4)/2) %>%
  ungroup() %>%
  select(-ecoregion, -year) %>%
  distinct() %>%
  mutate(total.burned = cbi.2 + cbi.3 + cbi.4,
         prop.burned = total.burned/sp.area,
         prop.cbi.4 = cbi.4/sp.area,
         C_NAME = fct_reorder(as.factor(C_NAME), desc(prop.burned))) %>%
  ungroup() %>%
  arrange(desc(prop.burned)) %>%
  slice_tail(n = 445) %>%
  mutate(filename = str_c(tolower(CWHR_ID), ".tif")) %>%
  select(filename)

plan(multisession, workers = 4)
future_pwalk(list(cumu.jobs$filename), cumu_area_stats)

cumu.out <- list.files(here("results", "cumu-area-output")) 

cumu.results <- as_tibble(cumu.out) %>%
  rename(filename = value) %>%
  mutate(temp.str = str_split_fixed(filename, "_", n = 2)) %>%
  mutate(CWHR_ID = toupper(str_sub(temp.str[,1], start = 1, end = -5)), 
         cbi.1 = NA, cbi.2 = NA, cbi.3 = NA, cbi.4 = NA) %>%
  select(-temp.str)

for (i in 1:nrow(cumu.results)) {
  temp <- read_csv(here("results", "cumu-area-output", cumu.out[i]))
  cumu.results$cbi.1[i] <- unlist(temp[1,])
  cumu.results$cbi.2[i] <- unlist(temp[2,])
  cumu.results$cbi.3[i] <- unlist(temp[3,])
  cumu.results$cbi.4[i] <- unlist(temp[4,])
}

write_csv(cumu.results, here("results", "results_cumu_raw.csv"))
```

## quality for 2020/21
```{r}
ecoregions <- read_csv(here("results", "results_ecoregion_metadata.csv"))
cumu.qual.jobs <- ecoregions %>%
  group_by(CWHR_ID) %>% 
  mutate(filename = str_c(tolower(CWHR_ID), ".tif")) %>%
  ungroup() %>%
  select(filename) %>%
  distinct() 

cumu_qual_stats <- function(sp.in) {
  sp <- rast(here("data", "output_data", "hab-suit-post-4", sp.in))
  cbi4 <- rast(here("data", "output_data", "ravg", "cbi4_ca-brick_202021_mosaic.tif"))
	qual.rast <- mask(sp, cbi4, maskvalues = c(NA, 0))
  stats <- global(qual.rast, fun = "mean", na.rm = T)
  write_csv(stats, here("results", "cumu-qual-output", str_c(sp.in, "_cumu_qual", ".csv")))
}

plan(multisession, workers = 4)
future_pwalk(list(cumu.qual.jobs$filename), cumu_qual_stats)

cumu.qual.out <- list.files(here("results", "cumu-qual-output")) 

cumu.qual.results <- as_tibble(cumu.qual.out) %>%
  rename(filename = value) %>%
  mutate(temp.str = str_split_fixed(filename, "_", n = 2)) %>%
  mutate(CWHR_ID = toupper(str_sub(temp.str[,1], start = 1, end = -5)), 
         cbi.1 = NA, cbi.2 = NA, cbi.3 = NA, cbi.4 = NA) %>%
  select(-temp.str)

for (i in 1:nrow(cumu.qual.results)) {
  temp <- read_csv(here("results", "cumu-qual-output", cumu.qual.out[i]))
  cumu.qual.results$cbi.1[i] <- unlist(temp[1,])
  cumu.qual.results$cbi.2[i] <- unlist(temp[2,])
  cumu.qual.results$cbi.3[i] <- unlist(temp[3,])
  cumu.qual.results$cbi.4[i] <- unlist(temp[4,])
}

write_csv(cumu.qual.results, here("results", "results_cumu_qual_raw.csv"))
```