---
title: "clipping bodies of water out of habitat suitability maps"
author: "Jessalyn Ayars"
date: '2022-04-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
library(tidyverse)
library(terra)
library(sf) 
library(spData)
select <- dplyr::select
```

1. mask out bodies of water
2. mask out the ocean
3. write to hab-suit-land
4. zip the originals

```{r data-loading}
sp.list <- read_csv(here("data", "output_data", "species-metadata-final.csv"))
file.list <- sp.list %>%
  mutate(code = tolower(CWHR_ID)) %>% 
  mutate(code = str_c(code, ".tif")) %>%
  select(code) %>%
  unlist()
lakes.n.reservoirs <- st_read(here("data", "raw_data", "NHD_Major_Lakes_and_Reservoirs.shp")) %>%
  st_transform(3310) %>%
  vect() 
ca <- filter(us_states, NAME == "California") %>% 
  st_transform(3310) %>%
  vect()
cbi4.ex <- rast(here("data", "output_data", "ravg", "cbi4_ca-brick_2021.tif"))
```

## Complete processing (too big for desktop to run in series)
```{r}
for (i in 1:length(file.list)) {
  temp0 <- rast(here("data", "output_data", "hab-suit", file.list[i]))
  if (class(temp0) == "SpatRaster") {
    temp1 <- mask(temp0, lakes.n.reservoirs, inverse = T)
    temp2 <- mask(temp1, ca)
    temp3 <- project(temp2, cbi4.ex)
    temp4 <- terra::resample(temp3, cbi4.ex, "ngb")
    writeRaster(temp4, here("data", "output_data", "hab-suit-land", file.list[i]), overwrite = T)
  } else {
    print(file.list[i], " dne")
  }
}
```

## List for CHTC
Use same list for other steps
```{r}
sp.list <- read_csv(here("data", "output_data", "species-metadata-final.csv"))
file.list <- sp.list %>%
  mutate(code = tolower(CWHR_ID)) %>% 
  mutate(code = str_c(code, ".tif")) %>%
  select(code) %>%
  unlist()
sp.cleaning <- file.list %>%
  as_tibble() %>%
  mutate(tif = str_c(value, ".tif")) %>%
  mutate(tfw = str_c(value, ".tfw")) %>%
  mutate(aux = str_c(value, ".tif.aux.xml")) %>%
  select(tif, tfw, aux, value) 

files <- list.files(here("data", "output_data", "hab-suit"), pattern = ".tif.tif")
good <- which(str_sub(files, -4, -1) == ".tif")

files.post <- files[good] %>% as_tibble() %>%
  mutate(size = file.size(here("data", "output_data", "hab-suit", value))) %>%
  mutate(mem = round(size* 4.000156e-06 + 2000), 1) %>%
  mutate(disk = round(size*7.755857e-05 + 1000), 1)

sp.cleaning.2 <- left_join(sp.cleaning, files.post, by = c("tif" = "value")) %>%
  select(-size, -`1`)
write_csv(sp.cleaning.2, here("code", "chtc-sp-cleaning.txt"), col_names = F)
```

### Quality control
- crs = crs of CBI4
- extent = extent of CBI4
- range <= 100
- exists
```{r qc}
final <- list.files(here("data", "output_data", "hab-suit-post-4")) %>% as_tibble()
for (i in 1:644) {
  if (tryCatch({rast(here("data", "output_data", "hab-suit-post-4", final$value[i])); TRUE}, error = function(e) FALSE)) {
    temp <- rast(here("data", "output_data", "hab-suit-post-4", final$value[i]))
    if (crs(temp) != crs(cbi4.ex)) {
      print(str_c(final$value[i], " has the wrong CRS"))
    }
    if (is.na(temp@ptr$range_max) | is.na(temp@ptr$range_min) | round(temp@ptr$range_max) > 100 | round(temp@ptr$range_min) < 1) { 
      print(str_c(final$value[i], " has a range of ", temp@ptr$range_min, " - ", temp@ptr$range_max))
    }
    if (xmin(temp) != xmin(cbi4.ex) | ymin(temp) != ymin(cbi4.ex)) {
      print(str_c(final$value[i], " has the wrong extent"))
    }
  } else {
    print(str_c(final$value[i], " is not readable as a raster"))
  }
}
```
